Курсовая работа по теме \\ \Huge{«Методы оптимизации»}

### 2009-12-18 simplex-method.tkz.tex
Lighter lines
No pattern

      % Set of feasible solutions
      \addplot[thick,draw=black,mark=none,pattern=dots]
      coordinates{(0,0) (0,2) (2,3.5) (5,0)} \closedcycle;
      \label{plot:simplex-feasible-space}

@@

      % Minimization process
      \addplot[line width=2pt, arrows=-triangle 45] coordinates{(0, 0) (0, 2)};
      \addplot[line width=2pt, arrows=-triangle 45] coordinates{(0, 2) (2,3.5)};
    \end{axis}
  \end{tikzpicture}
  \caption[Симплекс-метод]{Ход решения задачи \eqref{eq:lp-simple}
    симплекс-методом}
  \label{fig:simplex-method}
\end{figure}

>>>>

      % Set of feasible solutions
      \addplot[thick,draw=black,mark=none]
      coordinates{(0,0) (0,2) (2,3.5) (5,0)} \closedcycle;
      \label{plot:simplex-feasible-space}

@@

      % Minimization process
      \addplot[line width=1.5pt, arrows=-triangle 45] coordinates{(0, 0) (0, 2)};
      \addplot[line width=1.5pt, arrows=-triangle 45] coordinates{(0, 2) (2,3.5)};
    \end{axis}
  \end{tikzpicture}
  \caption[Симплекс-метод]{Ход решения задачи \eqref{eq:lp-simple}
    симплекс-методом}
  \label{fig:simplex-method}
\end{figure}
